Optimizing Structural Properties Of Neural Networks With Genetic Algorithms

### 2015-07-31 paper/paper.tex

To get a simple criterion to estimate whether it might be possible to learn a given function 
using FORCE with 100 neurons, we look at

>>>>

To get a simple criterion to estimate whether it might be possible to learn a given function 
using FORCE with 100 neurons, we look at a single sinusoidal of frequency $\omega$ and 
determine the range of $\omega$ in which an (unoptimized) network (i.e. GAIN, 
FEEDBACK, p, Erdös Renyi) is able to learn the function (see fig. \ref{}).
